---
title: "Trace Gas Chemistry"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Trace_Gas_Chemistry}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

To begin, we’ll load `foqat` and show three datasets in `foqat`:   
`voc` is a dataset about time series of volatile organic compounds with 1-hour resolution.   

```{r setup}
library(foqat)
head(voc)
```

## Convert VOC unit and analyse VOC concentration 

`vocct()` allows you to convert unit of VOCs between micrograms per cubic meter (ugm) and parts per billion by volume (ppbv); conduct statistics of VOC concentrations.  
You need to set `unit` into "ugm" or "ppbv". "ugm" means ug m~-3~. "ppbv" means part per billion volumn.  

```{r}
voc_con=vocct(voc, unit = "ppbv")
summary(voc_con)
```

`MW_Result` is the matched Molecular Weight (MW) value results.  

```{r}
voc_con[["MW_Result"]]
```

`Con_ugm` is time series of VOC mass concentrations by species.  

```{r}
head(voc_con[["Con_ugm"]])
```

`Con_ugm_stat` is the statistics of VOC mass concentration by species.  

```{r}
voc_con[["Con_ugm_stat"]]
```

`Con_ugm_group` is the time series of VOC mass concentration classified by groups.  

```{r}
head(voc_con[["Con_ugm_group"]])
```

`Con_ugm_group_stat` is the statistics of VOC mass concentration according to major groups.  

```{r}
voc_con[["Con_ugm_group_stat"]]
```

`Con_ppbv` is the time series of VOC volume concentration by species.
```{r}
head(voc_con[["Con_ppbv"]])
```

`Con_ppbv_stat` is the statistics of VOC volume concentration by species.  

```{r}
voc_con[["Con_ppbv_stat"]]
```

`Con_ppbv_group` is the time series of VOC volume concentration according to major groups.  

```{r}
head(voc_con[["Con_ppbv_group"]])
```

`Con_ppbv_group_stat` is the time series of VOC volume concentration classified by groups.  

```{r}
voc_con[["Con_ppbv_group_stat"]]
```


## Calculate ozone formation potential  

The `ofp()` allows you to statistics time series:  

```{r}
voc_ofp=ofp(voc)
summary(voc_ofp)
```

`MIR_Result` is the matched MIR value results.  

```{r}
voc_ofp[["MIR_Result"]]
```

`OFP_Result` is the OFP time series of VOC by species.  

```{r}
head(voc_ofp[["OFP_Result"]])
```

`OFP_Result_stat` is the statistics of OFP of VOC by species.  

```{r}
voc_ofp[["OFP_Result_stat"]]
```

`OFP_Result_group` is the time series of VOC classified by groups.  

```{r}
head(voc_ofp[["OFP_Result_group"]])
```

`OFP_Result_group_stat` is the statistics of OFP of VOC according to major groups.  

```{r}
voc_ofp[["OFP_Result_group_stat"]]
```

## Calculate OH reactivity  

The `loh()` allows you to statistics time series:

```{r}
voc_loh=loh(voc)
summary(voc_loh)
```

`KOH_Result` is the matched KOH value results.  

```{r}
voc_loh[["KOH_Result"]]
```

`LOH_Result` is the LOH time series of VOC by species.

```{r}
head(voc_loh[["LOH_Result"]])
```

`LOH_Result_stat` is the statistics of LOH of VOC by species.  

```{r}
voc_loh[["LOH_Result_stat"]]
```

`LOH_Result_group` is the LOH time series of VOC classified by groups.  

```{r}
head(voc_loh[["LOH_Result_group"]])
```

`LOH_Result_group_stat` is the statistics of LOH of VOC according to major groups.  

```{r}
voc_loh[["LOH_Result_group_stat"]]
```

## Get K~OH~  

The `koh()` allows you Searches K~OH~ value from 'chemspider.com'.

```{r}
koh("propene")
```











